Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-07-31 manuscripts/manuscript.Rmd
whoa, ggplot2 labeller started labeling incorrectly...

labeller <- function(variable,value){
    return(relabel[value])
}

@@

assume <- levels(as.factor(hist_dat$Assumption))
labeller <- function(variable,value){
if (variable=='penalty_fn') {
    return(relabel[value])
  } else {
    return(assume[value])
  }
}

>>>>

labeller <- function(variable,value){
    return(relabel[paste(value)])
}

@@

assume <- levels(as.factor(hist_dat$Assumption))
labeller <- function(variable,value){
if (variable=='penalty_fn') {
    return(relabel[paste(value)])
  } else {
    return(assume[paste(value)])
  }
}
